Untitled

### 2019-08-23 IPCO_NS.Rmd
updated

@@

```{r , include=FALSE}
plotarrays(k.coa, arraylabels=mnd.class)

@@

k.coa2<-ord(inferred_MetaCyc, classvec=mnd.class)
p <- plot(k.coa2)

@@

#plot(k.bga, genelabels=gene.symbs)    need to define gene;symbs

@@

p <- plot_ly(inferred_MetaCyc = volcano, type = "heatmap")

levelplot(inferred_MetaCyc[1:ncol(inferred_MetaCyc),ncol(inferred_MetaCyc):1])

>>>>

Things to complete in this script:

1. group the pathways

2. Will this tidy up the figures?

3. tidy up the figures anyway!

4. stats

@@

```{r , include=FALSE}
#   plotarrays(k.coa, arraylabels=mnd.class)

@@

k.coa2<-ord(inferred_MetaCyc, classvec=mnd.class)
p <- plot(k.coa2)
```

@@

#plot(k.bga, genelabels=gene.symbs)    need to define gene;symbs
```

@@

library(pheatmap)

pheatmap(inferred_MetaCyc)

pheatmap(inferred_MetaCyc, cluster_cols = mnd.class)
